The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-10-01 paper2_JNLS/paper.tex
NM

The purpose of the present manuscript is to expand upon the laboratory experiments of Bolles et al.~\cite{bolles2019anomalous} and the theoretical analysis of Majda et al.~\cite{majda2019statistical, majdaqi2019}, with special emphasis placed on the synergy between experiments and theory. We present a range of previously unpublished experimental data which motivates further refinement of the theory. Likewise, new theoretical predictions have motivated additional experimental measurements, and we present a comparison between the two. This close cooperation between theory and experiments has proven a successful strategy \cite{camassa2012stratified, ristroph2012, ganedi2018equilibrium}

% New data: slopes, autocorrelation, depth ratio varied.
% We also expand on the theoretical treatment of \cite{majda2019statistical}, with emphasis on more direct link to experiments.

% combination; draw close comparison; with an even closer comparison between theoretical predictions and experimental measurements.

% More careful development of theory and experiments, *in conjunction* with one another.

% Definitely cite several of Sapsis's new papers.

\vsp{4}

The purpose of this manuscript is to:
\begin{itemize}
\item Provide a more comprehensive treatment of the experiments and theory in combination. In particular, we make new comparisons between theory and experiments, which further confirm the predictive power of the theoretical framework.
\item Provide more thorough treatment of the link between physical system parameters and model parameters. This will elucidate the connection between theory and experiments. In particular, we flesh out details of non-dimensionalization, which were only briefly discussed in \cite{majda2019statistical} for the sake of brevity.
%more transparent connection to experimental parameters
\item Provide additional experimental measurements not presented in \cite{bolles2019anomalous}. For example, statistics on surface slope and autocorrelation.
\end{itemize}

>>>>

The purpose of the present manuscript is to expand upon the laboratory experiments of Bolles et al.~\cite{bolles2019anomalous} and the theoretical analysis of Majda et al.~\cite{majda2019statistical, majdaqi2019}, with special emphasis on the synergy between experiments and theory. We present an assortment of previously unpublished experimental data, for example on surface slope statistics and autocorrelation, which motivates further refinement of the theory. Likewise, novel theoretical predictions have motivated additional experimental measurements, and we present a comparison between the two. This close cooperation between theory and experiments has proven a successful strategy \cite{camassa2012stratified, ristroph2012, ganedi2018equilibrium}.

The purpose of this manuscript is to:
\begin{itemize}
\item Provide a more comprehensive treatment of the experiments and theory in combination. In particular, we make new comparisons between theory and experiments, which further confirm the predictive power of the theoretical framework.
\item Provide more thorough treatment of the link between physical system parameters and model parameters. This will elucidate the connection between theory and experiments. In particular, we flesh out details of non-dimensionalization, which were only briefly discussed in \cite{majda2019statistical} for the sake of brevity. 
\item Misc: We also expand on the theoretical treatment of \cite{majda2019statistical}, with emphasis on more direct link to experiments.
We give a more transparent connection to experimental parameters. More careful development of theory and experiments, *in conjunction* with one another.
\item Misc: combination; draw close comparison; with an even closer comparison between theoretical predictions and experimental measurements.
\end{itemize}

% New data: slopes, autocorrelation, depth ratio varied.
% Definitely cite several of Sapsis's new papers.
